Parenting Observation Experiment 2 Lexical Diversity Analysis

### 2019-03-01 paper/cogsci2019/cogsci2019.Rmd
writing

Young children spend a large portion of their waking time at play, variously manipulating objects, exploring their environment, and interacting with caregivers and peers.
Playing with objects allows them to discover hidden object properties and relations, and to build a causal understanding of how objects interact [e.g., @Schulz2007]. 
Meanwhile, play also gives children an opportunity to set and achieve goals (e.g., build a tower) and to practice a wide range of motor skills (e.g., stacking) that will help them navigate the world [@Singer2006].
Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events such as failures [@Singer2006].
Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
Early parenting practices have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
While many interventions have trouble reaching the parents of very young children, digital delivery of parenting advice by way of

>>>>

Young children spend a large portion of their waking time at play, variously manipulating objects, exploring their environment, and interacting with caregivers and peers.
Playing with objects allows them to discover hidden object properties and relations, and to build a causal understanding of how objects interact [e.g., @Schulz2007]. 
Meanwhile, play also gives children an opportunity to set and achieve goals (e.g., build a tower) and to practice a wide range of motor skills (e.g., stacking) that will help them navigate the world [@Singer2006].
Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events such as failures [@Singer2006].
Of course, young children are rarely playing in isolation: caregivers often provide encouragement and guidance while scaffolding a child's play [@Kaye1970; @Wood1976]. 
Indeed, parenting practices early in childhood have been shown to play an important role in shaping the future outcomes of young children [@Hart1995; @Heckman2006]. 
While interventions often have trouble reaching many parents of very young children, the proliferation of mobile devices offers a good avenut for the digital delivery of parenting advice [@Breitenstein2014].

### 2019-03-01 parenting_obs_e2/Lexical_Diversity_Analysis.Rmd
integrated lexical diversity graphs for both Exp 1 and Exp 2
writing

```{r echo=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache = TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)

@@

@@

###Sentence Length by age
(Maybe do a scatterplot with continuous scatterplot)

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(fig.width=8, fig.height=5, 
                      echo=TRUE, warning=FALSE, message=FALSE, cache = TRUE)
suppressPackageStartupMessages(c("dplyr","langcog","tidyr","ggplot2","lme4"))
library(psych)
library(langcog)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)

@@

# age is "1" or "2", but should be continuous value (in mos)
d$age = as.numeric(d$age)
d$Condition <- factor(d$condition, levels=c("con","exp"), labels=c("Control","Video"))
save(d, file="Exp2_cleaned_data.Rdata")
```

@@

###Sentence Length by age
(Maybe do a scatterplot with continuous age)
